Large-scale harmonic patterns clustering

### 2010-03-11 Paper/Paper.tex
improvements

% Three addresses
% --------------
\threeauthors
  {First author} {Affiliation1 \\ {\tt author1@ismir.edu}}
  {Second author} {\bf Retain these fake authors in\\\bf submission to preserve the formatting}
  {Third author} {Affiliation3 \\ {\tt author3@ismir.edu}}
% what order do we use? Thierry, Ron, Dan? is Juan on?

\begin{document}
%
\maketitle
%
\begin{abstract}
We present a method for discovering typical patterns in music.
Similar to the \textit{shingle} idea, but done on a larger scale through
Echo Nest API, we cluster harmonic patterns from 43K songs. Patterns are
made of ordered chroma features, and not of summarization like gaussian
mixtures coefficients or NMF weights. We explain
how to operate on such large datasets, we analyze the obained clusters,
and we discuss there use for retrieval and encoding. All code is made
available.\\
TAKE-HOME MESSAGE: \textit{Shingles} idea can go large-scale?
\end{abstract}
%
\section{Introduction}\label{sec:introduction}

@@

A major component of this work is scalability. We experiment with a training
set of $43$ thousands song, but everything scales linear in time
relative to the number of samples. We could imagine, as an extension
of this work, an algorithm ``listening'' to all music it can find online.
Time would be an issue, but not memory.

>>>>

% Three addresses
% --------------
\threeauthors
  {First author} {Affiliation1 \\ {\tt author1@ismir.edu}}
  {Second author} {\bf Retain these fake authors in\\\bf submission to preserve the formatting}
  {Third author} {Affiliation3 \\ {\tt author3@ismir.edu}}
% what order do we use? Thierry, Ron, Dan? is Juan on? is Graham on?

\begin{document}
%
\maketitle
%
\begin{abstract}
We present a method for discovering typical patterns in music.
Following up on the \textit{Shingle} idea, we bring these harmonic patterns
into the clustering framework. We use EchoNest API and a training set
of $43$K songs to assert our method. We restrain ourselves to an online
algorithm, thus it can scale to arbitrary data sizes.
We assess the basic good behaviours of our algorithm on this harmonic
data. We explain how to interpret the centroids of the clusters through
visualization and further encoding. We discuss ways to move to even larger
scales and we provide our code for reproducing the results.
TAKE-HOME MESSAGE: \textit{Shingles} idea can go large-scale?
\end{abstract}
%
\section{Introduction}\label{sec:introduction}

@@

A major component of this work is scalability. We experiment with a training
set of $43$ thousands song, but everything scales linear in time
relative to the number of samples. We could imagine, as an extension
of this work, an algorithm ``listening'' to all music it can find online.
Training time would be an issue, but not memory.
